\documentclass[12pt]{article}
\usepackage[usenames]{color} %used for font color
\usepackage{amsmath, amssymb, amsthm}
\usepackage{wasysym}
\usepackage[utf8]{inputenc} %useful to type directly diacritic characters
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{float}
\usepackage{mathtools}
\usepackage [english]{babel}
\usepackage [autostyle, english = american]{csquotes}
\MakeOuterQuote{"}
\graphicspath{ {./} }
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\prob}{\mathbb{P}}
\newcommand{\degrees}{^{\circ}}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

\author{Tianshuang (Ethan) Qiu}
\begin{document}
\title{Philosophy 12, Problem Set 1}
\maketitle
\newpage

\section{What is Prop. Logic?}
\subsection{Q1.0}
\begin{itemize}
    \item If you are taking this class, then you are a Berkeley student.
    \item It is not the case that you are taking this class.
    \item Therefore it is not the case that you are a Berkeley student.
\end{itemize}
This is not a good argument since there are a lot of Berkeley students who 
are not in this class.

\subsection{Q1.1}
\begin{itemize}
    \item It is more likely that I go running than that I do my homework.
    \item I am at least as likely to do my homework than it is that it rains tomorrow.
    \item Therefore it is more likely that I go running than it is that it rains..
\end{itemize}
This is a good argument, the conclusion logically follows from the premise ($p > q \geq r$, so $p > r$).

\section{Truth-Functional Connectives}
\subsection{Q2}

\begin{tabular}{ | c | c | c |}
    \hline
    $p$ & Pete heard that $p$ \\
    \hline
    TRUE & Maybe (didn't hear it) \\
    \hline
    FALSE & Maybe (false rumors) \\
    \hline
\end{tabular}
\newline
As we can see, the truth table cannot be written because the truth value of 
"Pete heard that $p$" does not only depend on $p$
    
\subsection{Q3}

\begin{tabular} {|c|c|c|}
    \hline
    Kate in library & Kate in gym & Kate in neither library nor gym \\
    \hline
    TRUE & TRUE & FALSE \\
    \hline
    TRUE & FALSE & FALSE \\
    \hline
    FALSE & TRUE & FALSE \\
    \hline
    FALSE & FALSE & TRUE \\
    \hline
\end{tabular}
\newline
The truth table is written above. The connective's value depends only on the operand's. 
Therefore it is truth functional.

\section{The Truth-Functional Conditional}
\subsection{Q4}
\textbf{Statement 1}: If I am not playing tennis, then I am watching tennis.
\newline
\textbf{Statement 2}: If it is not the case that I am watching tennis, then I am reading about tennis.
Since we can only do one activity at a time, we have the following truth table.
\newline
\begin{tabular}{|c|c|c|}
    \hline 
    Playing Tennis & Watching Tennis & Reading about Tennis \\
    \hline
    TRUE & FALSE & FALSE \\
    \hline
    FALSE & TRUE & FALSE \\
    \hline
    FALSE & FALSE & TRUE \\
    \hline
\end{tabular}
\newline
The first line is invalid since he is not watching tennis AND not reading about tennis, 
contradicting Statement 2.
\newline
The second line is valid since it satisfies both statements.
\newline
The thrid line is invalid since he is not watching tennis AND not watching tennis, contradicting 
Statement 1.

\subsection{Q5}
\begin{tabular}{|c|c|c|}
    \hline 
    Person is actually a knight & Statement is True  & Is there Gold \\
    \hline
    TRUE & TRUE & TRUE \\
    \hline
    FALSE & FALSE & ? \\
    \hline
\end{tabular}
\newline
The trivial part is if we have already met a knight, then he tells us 
the truth and there is gold on the island. 
\newline
The knave's case is more interesting, he lies and this statement is false. Therefore the predicate must be true 
and the conclusion false. However the only way for the predicate to be true is 
if he is a knight, which is a contradiction. Therefore this case is not possible.
\newline
Since the knave's case is not logically possible, we must have met a knight and there is gold on the island.

\section{Valid Forms of Argument I}
\subsection{Q6.1}
Let $p$ be "rabbits are fish."
\newline
Let $q$ be "mice are fish."
\newline
Let $r$ be "unicors exist."

\begin{itemize}
    \item $p \implies q$
    \item $q \implies r$
    \item $p \implies r$
\end{itemize}
The argument is valid but unsound. When $p$ is true, $q$ is also true, 
and thus $r$ is always true. However it is not sound since $p$ is always false.

\subsection{Q6.2}
Let $p$ be "rabbits are fish."
\newline
Let $q$ be "mice are fish."
\newline
Let $r$ be "unicorns exist."

\begin{itemize}
    \item $p \lor q$
    \item $p \lor r$
    \item $p \land (q \lor r)$
\end{itemize}
We can distribute the and operator to get $(p \land q) \lor (p \land r)$, 
which is not equal to both our premises ($(p \lor q) \land (p \lor r)$).
Therefore it invalid and unsound.

\section{Valid Forms of Argument II}
\subsection{Q7.1}

\begin{tabular}{|c|c|c|c|c|c|}
    \hline 
    $q$ & $\neg q$ & $q \lor \neg q$ & $r$ & $p$ & $\neg r \implies \neg p$ \\
    \hline
    FALSE & TRUE & TRUE & TRUE & TRUE & $\text{FALSE} \implies \text{FALSE}$ \\
    \hline
\end{tabular}
\newline
$\text{FALSE} \implies \text{FALSE}$ is true since false implying anything is true. Thus here 
we have all the premises true, but the conclusion $q$ is false. Thus 
the argument is invalid.

\subsection{Q7.2}
\begin{tabular}{|c|c|c|c|c|c|}
    \hline
    $p$ & $q$ & $\neg p$ & $p \land \neg p$ & $\text{Statement 1} \implies q$\\
    \hline
    TRUE & TRUE & FALSE & FALSE & TRUE \\
    \hline
    TRUE & FALSE & FALSE & FALSE & TRUE \\
    \hline
    FALSE & TRUE & TRUE & FALSE & TRUE \\
    \hline
    FALSE & FALSE & TRUE & FALSE & TRUE \\
    \hline
\end{tabular}
\newline
Every row evavluates to true, and the conclusion is true.

\section{Validity and Soundness}
\subsection{Q8}
\subsubsection{Part i}
If I am in Berkeley, and if Berkeley is on Mars, then I am on Mars.

\subsubsection{Part ii}
If I am in Berkeley, and if New York City is on Mars, then I am on Earth.

\subsubsection{Parat iii}
This is not possible since sound arguments are valid and their premises are true.
Therefore there conclusion must be true.

\section{Syntax of the Prop. Language I}
\subsection{Q9}
\subsubsection{Part i}
Let $p$ be I will go to school.
\newline
Let $q$ be I get a cookie now.
\newline
Then we have $p \iff q$

\subsubsection{Part ii}
Let $p$ be John is running.
\newline
Let $q$ be Mary is running.
\newline
Then we have $p \and q$

\subsubsection{Part i}
Let $p$ be a foreign national is entitled to social security.
\newline
Let $q$ be he has legal employment.
\newline
Let $r$ be he has had legal employment less than three years ago.
\newline
Let $t$ be he is currently also employed abroad.
\newline
Then we have $((q \lor r) \land \neg t )\implies p$

\subsection{Q10}
\subsubsection{Part f}
Let $p$ be Shamik goes to work by car.
\newline
Let $q$ be Shamik goes to work by bike.
\newline
Let $r$ be Shamik goes to work by train.
\newline
Then we have $p \lor (q \land r)$

\subsubsection{Part g}
Let $p$ be the party is on.
\newline
Let $q$ be the weather is bad.
\newline
Let $r$ be too many are sick.
\newline
Then we have $(q \land r) \implies \neg p$

\subsubsection{h}
Let $p$ be Jasmine is going to school.
\newline
Let $q$ be it is raning.
\newline
Let $r$ be Seth is going to school.
\newline
Then we have $p \land (q \implies r)$

\subsubsection{i}
Let $p$ be it isn't summer.
\newline
Let $q$ be it is damp or cold.
\newline
Let $r$ be it is evening or night.
\newline
Then we have $p \land (q \implies r)$

\subsubsection{j}
Let $p$ be you do not help me.
\newline
Let $q$ be I need you.
\newline
Let $r$ be I will not help you.
\newline
Let $s$ be you need me.
\newline
Then we have $(q \implies p) \implies (s \implies r)$

\subsubsection{k}
Let $p$ you stay with me.
\newline
Let $q$ be I won't drink anymore.
\newline
Then we have $(q \implies p) \implies q$

\subsection{l}
Let $p$ be we are going.
\newline
Let $q$ be it is raining.
\newline
Then we have $q \implies \neg p$

\subsection{m}
Let $p$ be you do mean it.
\newline
Let $q$ be I don't believe you.
\newline
Then we have $\neg p \land (p \implies q)$

\end{document}